### 2020-07-28 paper/paper.tex
Update paper.tex
Table 2 title updated

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds (\verb ModelSelection.jl). The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

The objective of this paper is to introduce the main characteristics and comparative performance of a key layer of our methodology: the modified all-subset 
regression algorithm included in \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl}{GlobalSearchRegression.jl} (v1.0.3). As other available 
alternatives (like \href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{MuMin-pdredge} in R, or \href{https://www.researchgate.net/profile/
Pablo_Gluzmann/publication/264782750_Global_Search_Regression_A_New_Automatic_Model-selection_Technique_for_Cross-section_Time-series_and_Panel-data_Regressions/
links/53eed18a0cf23733e812c10d/Global-Search-Regression-A-New-Automatic-Model-selection-Technique-for-Cross-section-Time-series-and-Panel-data-Regressions.pdf?
origin=publication_detail}{GSREG} Stata alternatives), this Julia algorithm allows researchers to obtain the best model specification among all possible 
covariate/feature combinations - in terms of user defined information criteria-, but up to 3165 times faster than Stata and 197 times faster than R. \vskip 6pt

@@

Through the gsreg function of the \verb interface.jl  internal package, users set the appropriate database to be used, the general unrestricted model -GUM, which defines the search space- and additional options for model selection. With this information and complementary supporting functions and definitions provided by \verb strings.jl  -i.e. error messages-, \verb utils.jl  -i.e. equation formatting, combinatorial analysis, database manipulation, sorting results, etc.- and \verb gsreg_results.jl  -i.e. the structure to save estimation results-, the \verb core.jl  package perform the all-subset-regression algorithm explained in the pseudocode below, to obtain the following outputs: 1) a matrix -optionally exported to a csv file through \verb utils.jl-  including egression coefficients, selection criteria, observations and (optionally) t-test, residual tests, averaging-weights and out-of-sample metrics for every lternative model; 2) a text file -also displayed on screen- which contains the best model specification and (optionally) model averaging results in terms of he user-selected information criteria -see multiple examples in \verb runtest.jl-. \vskip 6pt
\break

@@

In table 1, we present a performance comparison of our GLobalSearchRegression Julia-package against its main alternatives: MuMin-pdredge and GSREG (written in  and Stata\footnote{The parallel version of Stata-GSREG is still under development. A preliminary version is available upon request from authors}, espectively).
Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz. Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/juliacon2019proceedings/reproducibility}{here}} \vskip 6pt

@@

However, for databases with 20 or more covariates, our Julia all-subset-regression code is always faster, irrespective of the number of observations or threads -up to 3165 times faster than STATA and 197 times faster than R-. Execution time differences exponentially increase with the number of covariates and slightly decrease with available observations. Moreover, Stata and R alternatives become unfeasible for databases with 25 or more covariates. For a confirmatory nalysis,in figure 2 we present execution-time kernel densities for the 20 covariates - 100 observations - 32 threads case, obtained from 300 independent non-cached) runs. Kernel results show that execution time differences are not an artifact obtained from noisy runs. Our Julia algorithm is consistently faster han R and Stata alternatives. \vskip 6pt

A detailed speed-up analysis is also available for the 25-covariate case. In figure 3, it's shown that our Julia all-subset-regression algorithm scales almost linearly for large databases -while the number of threads is not higher than the number of physical cores-. With small databases, Amdhal's law \cite{Amdahl1967}inputs change. Parallel tasks become lighter and speed-up efficiency degrades consistently with additional threads, because the marginal overhead cost of a larger environment creation is not overcompensated by parallelism gains obtained from additional threads. Notwithstanding, using only physical cores speed-up efficiency is always above 45 \%  -with an average of 84\% for 2, 4, 8 and 16 threads-.

@@

\begin{itemize}
    \item[•] $Q$ is a $N \times p$ matrix with $Q'Q=I$  ; and
    \item[•] $R$ a $p \times p$ upper triangular matrix.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[h]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl & R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \begin{tabnote}
    Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.
    \end{tabnote}
\end{table}

@@

Throughout the paper, it has been shown that execution-time gains are explained by multiple efficient strategies combined in \verb GlobalSearchRegression.jl  i.e. task parallelism, static load-balancing, coarse-grained granularity, static memory allocation, efficient shared array implementation, and OLS estimation using neat QR decompositions). However, the main 'explanatory variable' is the impressive speed-up in atomic operations obtained using the Julia language. \vskip 6pt

>>>>

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds (\verb ModelSelection.jl). The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.5). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

The objective of this paper is to introduce the main characteristics and comparative performance of a key layer of our methodology: the modified all-subset 
regression algorithm included in \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl}{GlobalSearchRegression.jl} (v1.0.5). As other available 
alternatives (like \href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{MuMin-pdredge} in R, or \href{https://www.researchgate.net/profile/
Pablo_Gluzmann/publication/264782750_Global_Search_Regression_A_New_Automatic_Model-selection_Technique_for_Cross-section_Time-series_and_Panel-data_Regressions/
links/53eed18a0cf23733e812c10d/Global-Search-Regression-A-New-Automatic-Model-selection-Technique-for-Cross-section-Time-series-and-Panel-data-Regressions.pdf?
origin=publication_detail}{GSREG} Stata alternatives), this Julia algorithm allows researchers to obtain the best model specification among all possible 
covariate/feature combinations - in terms of user defined information criteria-, but up to 3165 times faster than Stata and 197 times faster than R. \vskip 6pt

@@

Through the gsreg function of the \verb interface.jl  internal package, users set the appropriate database to be used, the general unrestricted model -GUM, which defines the search space- and additional options for model selection. With this information and complementary supporting functions and definitions provided by \verb strings.jl  -i.e. error messages-, \verb utils.jl  -i.e. equation formatting, combinatorial analysis, database manipulation, sorting results, etc.- and \verb gsreg_results.jl  -i.e. the structure to save estimation results-, the \verb core.jl  package perform the all-subset-regression algorithm explained in the pseudocode below, to obtain the following outputs: 1) a matrix -optionally exported to a csv file through \verb utils.jl-  including regression coefficients, selection criteria, observations and (optionally) t-test, residual tests, averaging-weights and out-of-sample metrics for every alternative model; 2) a text file -also displayed on screen- which contains the best model specification and (optionally) model averaging results in terms of he user-selected information criteria -see multiple examples in \verb runtest.jl-. \vskip 6pt
\break

@@

In table 1, we present a performance comparison of our GLobalSearchRegression Julia-package against its main alternatives: MuMin-pdredge and GSREG (written in  Stata\footnote{The parallel version of Stata-GSREG is still under development. A preliminary version is available upon request from authors}, espectively).
Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz. Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/juliacon2019proceedings/reproducibility}{here}} \vskip 6pt

@@

However, for databases with 20 or more covariates, our Julia all-subset-regression code is always faster, irrespective of the number of observations or threads -up to 3165 times faster than STATA and 197 times faster than R-. Execution time differences exponentially increase with the number of covariates and slightly decrease with available observations. Moreover, Stata and R alternatives become unfeasible for databases with 25 or more covariates. For a confirmatory analysis, in figure 2 we present execution-time kernel densities for the 20 covariates - 100 observations - 32 threads case, obtained from 300 independent (non-cached) runs. Kernel density results show that execution time differences are not an artifact obtained from noisy runs. Our Julia algorithm is consistently faster han R and Stata alternatives. \vskip 6pt

A detailed speed-up analysis is also available for the 25-covariate case. In figure 3, it's shown that our Julia all-subset-regression algorithm scales almost linearly for large databases -while the number of threads is not higher than the number of physical cores-. With small databases, Amdhal's law \cite{Amdahl1967} inputs change. Parallel tasks become lighter and speed-up efficiency degrades consistently with additional threads, because the marginal overhead cost of a larger environment creation is not overcompensated by parallelism gains obtained from additional threads. Notwithstanding, using only physical cores speed-up efficiency is always above 45\%  -with an average of 84\% for 2, 4, 8 and 16 threads-.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
 \centerline{\includegraphics[width=16cm]{kernels.png}} 
    \vspace{2mm}
  \caption{Execution time, speed-up and speed-up efficiency for the 20-covariate case using GlobalSearchRegression.jl}
\end{figure*}

\begin{figure*}[t]
 \centerline{\includegraphics[width=16cm]{juliaexe.PNG}} 
    \vspace{2mm}
  \caption{Execution time, speed-up and speed-up efficiency for the 25-covariate case using GlobalSearchRegression.jl}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
    \item[] $Q$ is a $N \times p$ matrix with $Q'Q=I$  ; and
    \item[] $R$ a $p \times p$ upper triangular matrix.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[htbp]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl & R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \begin{tabnote}
    Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.
    \end{tabnote}
\end{table}

@@

Throughout the paper, it has been shown that execution-time gains are explained by multiple efficient strategies combined in \verb GlobalSearchRegression.jl  (i.e. task parallelism, static load-balancing, coarse-grained granularity, static memory allocation, efficient shared array implementation, and OLS estimation using neat QR decompositions). However, the main 'explanatory variable' is the impressive speed-up in atomic operations obtained using the Julia language. \vskip 6pt
